---
output:
  github_document:
    html_preview: false
---

# farsPackage
Building R Packages - Week 4 Assignment

[![Build Status](https://travis-ci.org/abhinavcreed13/testRPackage.svg?branch=master)](https://travis-ci.org/abhinavcreed13/testRPackage)
```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```
FarsPackage helps in reading Fatality Analysis Reporting System(FARS) data file and perform some analysis on it. 
You can easily include this package using following command:
```{r}
library(farsPackage)
```

Once package is loaded, you can use following functions to summarize and visualize FARS data.

## Summarizing years of data

You can use following R command to summarize any FARS file data

```{r}
summarized_data <- fars_summarize_years(c(2013,2014,2015))
head(summarized_data)
```
This data represents the number of fatalities occurring in different months of provided years.

## Visualizing Summarized Data

To Visualize fatalities data on the basis of different states, you can use following R command:

```{r}
fars_map_state(state.num = 4, year=2013)
````
