---
title: "Using the `farsPackage`"
author: "Abhinav Sharma"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Using the `farsPackage`}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

FarsPackage helps in reading Fatality Analysis Reporting System(FARS) data file and perform some analysis on it. 
You can easily include this package using following command:
```{r}
library(farsPackage)
```

Once package is loaded, you can use following functions to summarize and visualize FARS data.

## Loading data

The function `system.file` is the key that will allow us to gain access to the 2013 to 2015 data within the package. Let's begin with the 2015 data.

```{r accessfarsdat}
### the following code reads access the accident_2015.csv.bz2 file in the folder extdata in package FARSread and save it as an R object named fars_2015
fars_2013 <- system.file("extdata", "accident_2013.csv.bz2", package = "farsPackage")
fars_2014 <- system.file("extdata", "accident_2014.csv.bz2", package = "farsPackage")
fars_2015 <- system.file("extdata", "accident_2015.csv.bz2", package = "farsPackage")

### copy the file from its folder and save it to the working directory
file.copy(from = fars_2013, to = getwd()) 
file.copy(from = fars_2014, to = getwd()) 
file.copy(from = fars_2015, to = getwd()) 
```

## Summarizing years of data

You can use following R command to summarize any FARS file data

```{r}
summarized_data <- fars_summarize_years(c(2013,2014,2015))
head(summarized_data)
```
This data represents the number of fatalities occurring in different months of provided years.

## Visualizing Summarized Data

To Visualize fatalities data on the basis of different states, you can use following R command:

```{r}
fars_map_state(state.num = 4, year=2013)
fars_map_state(state.num = 4, year=2014)
fars_map_state(state.num = 4, year=2015)
```

## Deleting data from working directory

Before we end, let's get read of the copy of the files we copied from the system directory to the working directory.

```{r deldat}
file.remove("./accident_2013.csv.bz2")
file.remove("./accident_2014.csv.bz2")
file.remove("./accident_2015.csv.bz2")
```
